Biogeography & environmental conditions shape bacteriophage & bacteria interaction networks across the human microbiome

### 2017-10-01 doc/manuscript.Rmd
Manuscript updates.
Updated manusript with format for new submission.

---
title: Biogeography & Environmental Conditions Shape Phage & Bacteria Interaction Networks Across the Human Microbiome
author:
- name: Geoffrey D Hannigan
  affiliation: 1
- name: Melissa B Duhaime
  affiliation: 2
- name: Danai Koutra
  affiliation: 3
- name: Patrick D Schloss
  affiliation: 1,\*
address:
  - code: 1
    address: Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan, 48109
  - code: 2
    address: Department of Ecology & Evolutionary Biology, University of Michigan, Ann Arbor, Michigan, 48109
  - code: 3
    address: Department of Computer Science, University of Michigan, Ann Arbor, Michigan, 48109
  - code: \*
    address: To whom correspondence may be addressed.
output:
  md_document:
    variant: markdown
fontsize: 12pt
mainfont: 'Helvetica'
---

@@

***Running Title***: Network Diversity of the Healthy Human Microbiome

@@

# Importance

@@

https://github.com/SchlossLab/Hannigan_ConjunctisViribus_mSystems_2017

@@

@@

# Disclosure Declaration
The authors report no conflicts of interest.

@@

# Figure Legends

# Supplemental Figure Legends

@@

# Supplemental Table Legend

>>>>

---
title: Biogeography & environmental conditions shape bacteriophage & bacteria interaction networks across the human microbiome
author:
- name: Geoffrey D Hannigan
  affiliation: 1
- name: Melissa B Duhaime
  affiliation: 2
- name: Danai Koutra
  affiliation: 3
- name: Patrick D Schloss
  affiliation: 1,\*
address:
  - code: 1
    address: Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan, 48109, USA
  - code: 2
    address: Department of Ecology & Evolutionary Biology, University of Michigan, Ann Arbor, Michigan, 48109, USA
  - code: 3
    address: Department of Computer Science, University of Michigan, Ann Arbor, Michigan, 48109, USA
  - code: \*
    address: To whom correspondence may be addressed.
output:
  md_document:
    variant: markdown
fontsize: 12pt
mainfont: 'Helvetica'
---

@@

***Short Title***: Network Diversity of the Healthy Human Microbiome

@@

# Author Summary

@@

https://github.com/SchlossLab/Hannigan_ConjunctisViribus_ploscompbio_2017

@@

# Author Contributions
*Conceptualization*: GDH, MBD, DK, PDS. *Data Curation*: GDH. *Formal Analysis*: GDH. *Funding Acquisition*: GDH, PDS. *Writing – Original Draft Preparation*: GDH, PDS. *Writing – Review & Editing*: GDH, MBD, DK, PDS.

@@

# Competing interests
The authors report no conflicts of interest.

@@

# Supplemental Figure Captions

@@

# Supplemental Table Captions
